\documentclass[11pt,oneside]{article}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage[T1]{fontenc}

\pagestyle{empty}
\geometry{letterpaper,tmargin=1in,bmargin=1in,lmargin=1in,rmargin=1in,headheight=0in,headsep=0in,footskip=.3in}
\hypersetup{colorlinks=true,pdfstartview={FitH},urlcolor=red}

\setlength{\parindent}{0in} \setlength{\parskip}{0in}
\setlength{\itemsep}{0in} \setlength{\topsep}{0in}
\setlength{\tabcolsep}{0in}

% Name and contact information
\newcommand{\name}{Hu Shijie (Stuart Hu)}
\newcommand{\phone}{Phone: 13917285414}
\newcommand{\email}{E-mail: \href{mailto:stuarthu2002@hotmail.com}{stuarthu2002@hotmail.com}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% New commands and environments

% This defines how the name looks
\newcommand{\bigname}[1]{
	\begin{center}\selectfont\Huge\scshape#1\end{center}
}

% A ressection is a main section (<H1>Section</H1>)
\newenvironment{ressection}[1]{
	\vspace{4pt}
	{\selectfont\Large#1}
	\begin{itemize}
	\vspace{3pt}
}{
	\end{itemize}
}

% A resitem is a simple list element in a ressection (first level)
\newcommand{\resitem}[1]{
	\vspace{-4pt}
	\item \begin{flushleft} #1 \end{flushleft}
}

% A ressubitem is a simple list element in anything but a ressection (second level)
\newcommand{\ressubitem}[1]{
	\vspace{-1pt}
	\item \begin{flushleft} #1 \end{flushleft}
}

% A resbigitem is a complex list element for stuff like jobs and education:
%  Arg 1: Name of company or university
%  Arg 2: Location
%  Arg 3: Title and/or date range
\newcommand{\resbigitem}[3]{
	\vspace{-5pt}
	\item
	\textbf{#1}---#2 \\
	\textit{#3}
}

% This is a list that comes with a resbigitem
\newenvironment{ressubsec}[3]{
	\resbigitem{#1}{#2}{#3}
	\vspace{-2pt}
	\begin{itemize}
}{
    \end{itemize}
}

% This is a simple sublist
\newenvironment{reslist}[1]{
	\resitem{\textbf{#1}}
	\vspace{-5pt}
	\begin{itemize}
}{
	\end{itemize}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Now for the actual document:

\begin{document}

% Name with horizontal rule
\bigname{\name}

\vspace{-8pt} \rule{\textwidth}{1pt}

\vspace{-1pt} {\small\itshape \phone \hfill \email}

\vspace{8 pt}


%%%%%%%%%%%%%%%%%%%%%%%%
\begin{ressection}{Education}

	\begin{ressubsec}{Shanghai Jiao Tong University}{Shanghai}{Master of Engineering in Information Security}
		\ressubitem{2006.2 -- 2008.12}
	\end{ressubsec}

	\begin{ressubsec}{Shanghai Jiao Tong University}{Shanghai}{Bachelor of Science in Electrical Engineering}
		\ressubitem{1999.9 -- 2003.7}
	\end{ressubsec}

\end{ressection}

%%%%%%%%%%%%%%%%%%%%%%%%
\begin{ressection}{Working Experience}

	\begin{ressubsec}{Scopely}{Shanghai, Jingan}{Senior Devops Engineer: 2021.7 -- now}
		\ressubitem{Creating engineer backend infrastructure on China AWS, including Gitlab instance/runners/CICD pipelines.}
		\ressubitem{Porting mobile game backend from AWS ECS to China Ucloud k8s, including storage/database/caches/message queues.}
		\ressubitem{Lead the server code merge process.}
		\ressubitem{Design and implement game content merge solution.}
		\ressubitem{Creating central monitoring system (grafana/prometheus) to monitor k8s and vm nodes metrics (CPU/memory usage) and game metrics.}
		\ressubitem{Daily operating and maintanence for the infrastructures, troubleshooting stability issues.}
	\end{ressubsec}

	\begin{ressubsec}{Baidu}{Shanghai, Zhangjiang}{T6: 2020.12 -- 2021.6}
		\ressubitem{Design and implement streaming computing platform.}
	\end{ressubsec}

	\begin{ressubsec}{Improbable}{Shanghai, 688 Plaza}{Senior Infrastructure Architect: 2019.5 -- 2020.11}
		\ressubitem{Porting SpatialOS from GKE to k8s cluster on China AWS. Switching GCR to ECR, GCE to EC2, Google IAM to AWS IAM. Using terraform to manage clusters.}
		\ressubitem{Create CICD pipelines on BuildKite, automatically rollout on testing/staging/production environment.}
		\ressubitem{Multiple knowledge sharing session inside China Infra team, like OAUTH introduction and Golang advanced topics.}
		\ressubitem{Architect, design and implement China Billing system.}
		\ressubitem{Member of API Guild, writing Improbable API Standard Proposals, push approval process.}
	\end{ressubsec}

	\begin{ressubsec}{Qiniu}{Shanghai, Zhangjiang}{Senior Developer: 2018.4 -- 2019.5}
		\ressubitem{Implemented NAS gateway protocols including NFS/FTP.}
		\ressubitem{Implemented Version Management for Qiniu's object storage.}
		\ressubitem{Implemented S3 gateway for Qiniu's object storage.}
		\ressubitem{Submitted 4 patents during work, application number: 201810813487.3, 201811227621.8, 201910124563.4, 201910124576.1}
	\end{ressubsec}

	\begin{ressubsec}{EMC}{Shanghai, KIC}{Principal Software Engineer: 2014.2 -- 2018.4}
		\ressubitem{Mozy Infra Team DEV Leader, lead 2 teams simultaneously, main responsibility includes: architecture design, feature design review, code review, solution investigation, POC research, coaching and managing team members.}
		\ressubitem{Quickly master new things like S3 protocol, Golang, Cloud Foundry, Cassandra and ElasticSearch, able to explain tech details to team members.}
		\ressubitem{Recognized as CE(consistently exceeds) in 2015, 2016 year end KPI review.}
	\end{ressubsec}

	\begin{ressubsec}{Nomura Information Technology}{Shanghai, Central Plaza}{Senior Developer: 2013.1 -- 2014.1}
		\ressubitem{Develop and maintain the position management system of Nomura Investment Bank.}
	\end{ressubsec}

	\begin{ressubsec}{SAP Labs China}{Shanghai, Zhangjiang}{Application Developer: 2007.9 -- 2013.1}
		\ressubitem{Working in inventory module for SAP Business One.}
	\end{ressubsec}

	\begin{ressubsec}{Accton Technology Corp}{Shanghai, Caohejing}{Senior Software Engineer: 2006.10 -- 2007.9}
		\ressubitem{Develop, maintain and test network protocol software such as MPLS, LDP and DVMRP on
			hybrid switch. Use pure C on VxWorks.}
	\end{ressubsec}

	\begin{ressubsec}{Pengyue Jinghong Technology Corp}{Shanghai, Zhangjiang}{Software Engineer: 2003.7 -- 2006.10}
		\ressubitem{Develop, maintain and test network security software in Linux. The main develop
			language is C/C++, part of WEB configuration module implemented with Perl and Bash.}
	\end{ressubsec}

\end{ressection}

\begin{ressection}{Skill Set}

	\begin{reslist}{Developer Expertise:}
		\ressubitem{Familiar with distributed object storage system, years of architecturing, designing, developing, deploying and on line bug investigation experience.}
		\ressubitem{Fully understanding of software development life cycle.}
		\ressubitem{Love problem solving.}
		\ressubitem{Good at coaching team members with technical direction and guidance.}
		\ressubitem{Strong sense of ownership and commitment, proactively take on new challenges with minimal supervision.}
	\end{reslist}

	\begin{reslist}{English:}
		\ressubitem{CET Band 6.}
		\ressubitem{10+ years of working in foreign companies like SAP and EMC, fluent communicating with colleagues overseas.}
	\end{reslist}

	\begin{reslist}{Operating System:}
		\ressubitem{10+ years on Linux, have a deep understanding of Linux architecture,
			fully understanding of Linux IPC, System Call and
			many other OS related stuffs such as timer, interrupt handling and process scheduling.}
		\ressubitem{6 years on Windows with Visual Studio.}
	\end{reslist}

	\begin{reslist}{Database:}
		\ressubitem{Excellent SQL/NOSQL programming.}
		\ressubitem{Familliar with Cassandra, ElasticSearch.}
	\end{reslist}

	\begin{reslist}{Programming Languages:}
		\ressubitem{Expert in C/C++/Golang.}
		\ressubitem{Proficient in Perl/Python/Ruby/Bash.}
	\end{reslist}

\end{ressection}

\begin{ressection}{Other Achievements}

	\begin{reslist}{Open Source Contribution:}
	        \ressubitem{Raise pull requests for GitHub projects like facebook/rocksdb, jetstack/cert-manager}
	\end{reslist}

	\begin{reslist}{Book Written:}
	        \ressubitem{\href{https://item.jd.com/60796801160.html}{Distributed Object Storage -- Pricipal, Architect and Go Implement}}
	        \ressubitem{\href{https://item.jd.com/12495484.html}{Distributed Cache -- Pricipal, Architect and Go Implement}}
	\end{reslist}

	\begin{reslist}{Book Translated:}
		\ressubitem{\href{https://www.epubit.com/book/detail/33175}{Principles of Object-Oriented JavaScript}}
		\ressubitem{\href{https://www.epubit.com/book/detail/15126}{Python and HDF5}}
		\ressubitem{\href{https://www.epubit.com/book/detail/14722}{High Performance Python}}
	\end{reslist}

\end{ressection}

\end{document}
